\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2016-12-20 doc/publications/plos16/plos16.tex
new times

\begin{table}[!ht]
\begin{minipage}{\textwidth}
\centering
\caption{ {\bf Performance comparison with \cursedforest\ on different subsets of the 1000 Genomes Project data.}}
\begin{tabular}{| l | r | l |}
\hline
{\bf Genome \%} & {\bf Error} & {\bf Runtime} \\ \thickhline
phase1\_chr22: 1,092 x 490,036 & 0.04 & 1 min 50 seconds \\ \hline
phase3\_chr22: 2,504 x 1,103,548 & 0.06 & 4 min 2 seconds \\ \hline
phase3\_chr1: 2,504 x 6,450,364 & 0.04 & 19 min 19 seconds \\ \hline
phase3\_chr1-3: 2,504 x 19,328,051 & 0.02 & 56 min 43 seconds \\ \hline
phase3\_chr1-22: 2,504 x 81,047,467 & 0.01 & 36 min 54 seconds \\ \hline
\end{tabular}
\begin{flushleft} 
Comparison of runtime and error for models built using \cursedforest\ on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees and was built using 130 worker nodes---each with 8GB RAM.
\end{flushleft}
\label{cursedforesttable}
\end{minipage}
\end{table}

>>>>

\begin{table}[!ht]
\begin{minipage}{\textwidth}
\centering
\caption{ {\bf Performance comparison with \cursedforest\ on different subsets of the 1000 Genomes Project data.}}
\begin{tabular}{| l | r | l |}
\hline
{\bf Genome \%} & {\bf Error} & {\bf Runtime} \\ \thickhline
phase1\_chr22: 1,092 x 490,036 & 0.04 & 1 min 5 seconds \\ \hline
phase3\_chr22: 2,504 x 1,103,548 & 0.06 & 1 min 37 seconds \\ \hline
phase3\_chr1: 2,504 x 6,450,364 & 0.04 & 4 min 10 seconds \\ \hline
phase3\_chr1-3: 2,504 x 19,328,051 & 0.02 & 10 min 49 seconds \\ \hline
phase3\_chr1-22: 2,504 x 81,047,467 & 0.01 & 36 min 54 seconds \\ \hline
\end{tabular}
\begin{flushleft} 
Comparison of runtime and error for models built using \cursedforest\ on different subsets of variant data 
from the 1000 Genomes Project.
Each random forest model consists of 50 trees and was built using 130 worker nodes---each with 8GB RAM.
\end{flushleft}
\label{cursedforesttable}
\end{minipage}
\end{table}
